The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-17 paper.tex
HUGE changes
added my name
added adams name
Removing cruft from the files. Adding makefile and .gitignore

	% DOI
	\doi{10.475/123_4}

	% ISBN
	\isbn{123-4567-24-567/08/06}

	%Conference
	\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

	\acmPrice{\$15.00}

	%
	% --- Author Metadata here ---
	\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
	%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
	%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
	% --- End of Author Metadata ---

	\title{E-jection fraction - Tracking how your website pumps out E-Mails}
	%
	% You need the command \numberofauthors to handle the 'placement
	% and alignment' of the authors beneath the title.
	%
	% For aesthetic reasons, we recommend 'three authors at a time'
	% i.e. three 'name/affiliation blocks' be placed beneath the title.
	%
	% NOTE: You are NOT restricted in how many 'rows' of
	% "name/affiliations" may appear. We just ask that you restrict
	% the number of 'columns' to three.
	%
	% Because of the available 'opening page real-estate'
	% we ask you to refrain from putting more than six authors
	% (two rows with three columns) beneath the article title.
	% More than six makes the first-page appear very cluttered indeed.
	%
	% Use the \alignauthor commands to handle the names
	% and affiliations for an 'aesthetic maximum' of six authors.
	% Add names, affiliations, addresses for
	% the seventh etc. author(s) as the argument for the
	% \additionalauthors command.
	% These 'additional authors' will be output/set for you
	% without further effort on your part as the last section in
	% the body of your article BEFORE References or any Appendices.

	\numberofauthors{8} %  in this sample file, there are a *total*
	% of EIGHT authors. SIX appear on the 'first-page' (for formatting
	% reasons) and the remaining two appear in the \additionalauthors section.
	%
	\author{
		% You can go ahead and credit any number of authors here,
		% e.g. one 'row of three' or two rows (consisting of one row of three
		% and a second row of one, two or three).
		%
		% The command \alignauthor (no curly braces needed) should
		% precede each author name, affiliation/snail-mail address and
		% e-mail address. Additionally, tag each line of
		% affiliation/address with \affaddr, and tag the
		% e-mail address with \email.
		%
		% 1st. author
		\alignauthor
		Ben Trovato\titlenote{Dr.~Trovato insisted his name be first.}\\
		\affaddr{Institute for Clarity in Documentation}\\
		\affaddr{1932 Wallamaloo Lane}\\
		\affaddr{Wallamaloo, New Zealand}\\
		\email{trovato@corporation.com}
		% 2nd. author
		\alignauthor
		G.K.M. Tobin\titlenote{The secretary disavows
			any knowledge of this author's actions.}\\
		\affaddr{Institute for Clarity in Documentation}\\
		\affaddr{P.O. Box 1212}\\
		\affaddr{Dublin, Ohio 43017-6221}\\
		\email{webmaster@marysville-ohio.com}
		% 3rd. author
		\alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
			one who did all the really hard work.}\\
		\affaddr{The Th{\o}rv{\"a}ld Group}\\
		\affaddr{1 Th{\o}rv{\"a}ld Circle}\\
		\affaddr{Hekla, Iceland}\\
		\email{larst@affiliation.org}
		\and  % use '\and' if you need 'another row' of author names
		% 4th. author
		\alignauthor Lawrence P. Leipuner\\
		\affaddr{Brookhaven Laboratories}\\
		\affaddr{Brookhaven National Lab}\\
		\affaddr{P.O. Box 5000}\\
		\email{lleipuner@researchlabs.org}
		% 5th. author
		\alignauthor Sean Fogarty\\
		\affaddr{NASA Ames Research Center}\\
		\affaddr{Moffett Field}\\
		\affaddr{California 94035}\\
		\email{fogartys@amesres.org}
		% 6th. author
		\alignauthor Charles Palmer\\
		\affaddr{Palmer Research Laboratories}\\
		\affaddr{8600 Datapoint Drive}\\
		\affaddr{San Antonio, Texas 78229}\\
		\email{cpalmer@prl.com}
	}
	% There's nothing stopping you putting the seventh, eighth, etc.
	% author on the opening page (as the 'third row') but we ask,
	% for aesthetic reasons that you place these 'additional authors'
	% in the \additional authors block, viz.
	\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
		email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
		(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
	\date{30 July 1999}
	% Just remember to make sure that the TOTAL number of authors
	% is the number that will appear on the first page PLUS the
	% number that will appear in the \additionalauthors section.

@@

	%
	% The code below should be generated by the tool at
	% http://dl.acm.org/ccs.cfm
	% Please copy and paste the code instead of the example below. 
	%
	\begin{CCSXML}
		<ccs2012>
		<concept>
		<concept_id>10010520.10010553.10010562</concept_id>
		<concept_desc>Computer systems organization~Embedded systems</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>10010520.10010575.10010755</concept_id>
		<concept_desc>Computer systems organization~Redundancy</concept_desc>
		<concept_significance>300</concept_significance>
		</concept>
		<concept>
		<concept_id>10010520.10010553.10010554</concept_id>
		<concept_desc>Computer systems organization~Robotics</concept_desc>
		<concept_significance>100</concept_significance>
		</concept>
		<concept>
		<concept_id>10003033.10003083.10003095</concept_id>
		<concept_desc>Networks~Network reliability</concept_desc>
		<concept_significance>100</concept_significance>
		</concept>
		</ccs2012>  
	\end{CCSXML}

	\ccsdesc[500]{Computer systems organization~Embedded systems}
	\ccsdesc[300]{Computer systems organization~Redundancy}
	\ccsdesc{Computer systems organization~Robotics}
	\ccsdesc[100]{Networks~Network reliability}

@@

	%
	%  Use this command to print the description
	%
	\printccsdesc

@@

	\keywords{ACM proceedings; \LaTeX; text tagging}

>>>>

	% DOI
	%\doi{10.475/123_4}

	% ISBN
	%\isbn{123-4567-24-567/08/06}

	%Conference
	%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

	%\acmPrice{\$15.00}

	%
	% --- Author Metadata here ---
	%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
	%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
	%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
	% --- End of Author Metadata ---

	%\title{E-jection fraction - Tracking how your website pumps out
	%E-Mails}
    \title{The Prevalence of E-Mail Header Injections on the World
      Wide Web}
	%
	% You need the command \numberofauthors to handle the 'placement
	% and alignment' of the authors beneath the title.
	%
	% For aesthetic reasons, we recommend 'three authors at a time'
	% i.e. three 'name/affiliation blocks' be placed beneath the title.
	%
	% NOTE: You are NOT restricted in how many 'rows' of
	% "name/affiliations" may appear. We just ask that you restrict
	% the number of 'columns' to three.
	%
	% Because of the available 'opening page real-estate'
	% we ask you to refrain from putting more than six authors
	% (two rows with three columns) beneath the article title.
	% More than six makes the first-page appear very cluttered indeed.
	%
	% Use the \alignauthor commands to handle the names
	% and affiliations for an 'aesthetic maximum' of six authors.
	% Add names, affiliations, addresses for
	% the seventh etc. author(s) as the argument for the
	% \additionalauthors command.
	% These 'additional authors' will be output/set for you
	% without further effort on your part as the last section in
	% the body of your article BEFORE References or any Appendices.

	\numberofauthors{1} %  in this sample file, there are a *total*
	% of EIGHT authors. SIX appear on the 'first-page' (for formatting
	% reasons) and the remaining two appear in the \additionalauthors section.
	%

    % Note: For CCS submission we need to have it anonymous

	\author{
		% You can go ahead and credit any number of authors here,
		% e.g. one 'row of three' or two rows (consisting of one row of three
		% and a second row of one, two or three).
		%
		% The command \alignauthor (no curly braces needed) should
		% precede each author name, affiliation/snail-mail address and
		% e-mail address. Additionally, tag each line of
		% affiliation/address with \affaddr, and tag the
		% e-mail address with \email.
		%
		% 1st. author
		%% \alignauthor
		%% Sai Prashanth Chandramouli\\
		%% \affaddr{Arizona State University}\\
		%% \email{saipc@asu.edu}
		%% % 2nd. author
		%% \alignauthor
		%% Adam Doup\'{e}\titlenote{The secretary disavows
		%% 	any knowledge of this author's actions.}\\
		%% \affaddr{Arizona State University}\\
		%% \email{doupe@asu.edu}
		%% % 3rd. author
		%% \alignauthor Lars Th{\o}rv{\"a}ld\titlenote{This author is the
		%% 	one who did all the really hard work.}\\
		%% \affaddr{The Th{\o}rv{\"a}ld Group}\\
		%% \affaddr{1 Th{\o}rv{\"a}ld Circle}\\
		%% \affaddr{Hekla, Iceland}\\
		%% \email{larst@affiliation.org}
		%% \and  % use '\and' if you need 'another row' of author names
		%% % 4th. author
		%% \alignauthor Lawrence P. Leipuner\\
		%% \affaddr{Brookhaven Laboratories}\\
		%% \affaddr{Brookhaven National Lab}\\
		%% \affaddr{P.O. Box 5000}\\
		%% \email{lleipuner@researchlabs.org}
		%% % 5th. author
		%% \alignauthor Sean Fogarty\\
		%% \affaddr{NASA Ames Research Center}\\
		%% \affaddr{Moffett Field}\\
		%% \affaddr{California 94035}\\
		%% \email{fogartys@amesres.org}
		%% % 6th. author
		%% \alignauthor Charles Palmer\\
		%% \affaddr{Palmer Research Laboratories}\\
		%% \affaddr{8600 Datapoint Drive}\\
		%% \affaddr{San Antonio, Texas 78229}\\
		%% \email{cpalmer@prl.com}
	}
	% There's nothing stopping you putting the seventh, eighth, etc.
	% author on the opening page (as the 'third row') but we ask,
	% for aesthetic reasons that you place these 'additional authors'
	% in the \additional authors block, viz.
	%% \additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
	%% 	email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
	%% 	(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
	%% \date{30 July 1999}
	% Just remember to make sure that the TOTAL number of authors
	% is the number that will appear on the first page PLUS the
	% number that will appear in the \additionalauthors section.

@@

	%
	% The code below should be generated by the tool at
	% http://dl.acm.org/ccs.cfm
	% Please copy and paste the code instead of the example below. 
	%
	%% \begin{CCSXML}
	%% 	<ccs2012>
	%% 	<concept>
	%% 	<concept_id>10010520.10010553.10010562</concept_id>
	%% 	<concept_desc>Computer systems organization~Embedded systems</concept_desc>
	%% 	<concept_significance>500</concept_significance>
	%% 	</concept>
	%% 	<concept>
	%% 	<concept_id>10010520.10010575.10010755</concept_id>
	%% 	<concept_desc>Computer systems organization~Redundancy</concept_desc>
	%% 	<concept_significance>300</concept_significance>
	%% 	</concept>
	%% 	<concept>
	%% 	<concept_id>10010520.10010553.10010554</concept_id>
	%% 	<concept_desc>Computer systems organization~Robotics</concept_desc>
	%% 	<concept_significance>100</concept_significance>
	%% 	</concept>
	%% 	<concept>
	%% 	<concept_id>10003033.10003083.10003095</concept_id>
	%% 	<concept_desc>Networks~Network reliability</concept_desc>
	%% 	<concept_significance>100</concept_significance>
	%% 	</concept>
	%% 	</ccs2012>  
	%% \end{CCSXML}

	%% \ccsdesc[500]{Computer systems organization~Embedded systems}
	%% \ccsdesc[300]{Computer systems organization~Redundancy}
	%% \ccsdesc{Computer systems organization~Robotics}
	%% \ccsdesc[100]{Networks~Network reliability}

@@

	%
	%  Use this command to print the description
	%
	% \printccsdesc

@@

	% \keywords{ACM proceedings; \LaTeX; text tagging}
